\documentclass[11pt]{article}

\usepackage[margin=1cm]{geometry}
\usepackage{titlesec}
\usepackage{setspace}
\usepackage{pifont}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{csquotes}
\usepackage{enumitem}
\usepackage{hyperref}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlist[itemize]{noitemsep}


\pagenumbering{gobble}

\titleformat{\section}{\large\bfseries}{\thesection.}{1em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection.}{1em}{}

% Section for experience
\newcommand{\experience}[4]{%
  \vspace{5pt}
  \textbf{#2} \hfill \textbf{#3} \\
  \textit{#1} \hfill \textit{#4} \\
  \vspace{-10pt}
}

% Bullet points for tasks and achievements
\newcommand{\bulletpoint}[1]{%
  \begin{itemize}
    \setlength\itemsep{-3pt}
    \setlength{\topsep}{0pt}
    \item #1
  \end{itemize}
}

\newcommand{\cvsection}[1]{%
  \section*{#1}
    \vspace{-10pt}
    \hrule
    \vspace{10pt}
}

\begin{document}

% Your header
\textbf{\Huge Martin STEFFEN} \textit{(he / him)}

\large{\href{mailto:mail@tiph.io}{mail@tiph.io} \ding{117} 00 33 6 23 88 36 13 \ding{117} \texttt{github.com/tiphedor} \ding{117} \texttt{tiph.io}}

\vspace{10pt}
\hrule
\vspace{15pt}


Software engineer with over five years of experience, known for adaptability and a strong passion for technology. Skilled in both front-end and back-end development, with additional expertise in cloud infrastructure, deployment, and automation. Comfortable working across diverse domains and always eager to learn and take on new challenges.

\cvsection{Professional Experience}


\experience{Senior full-stack developer}{Mindflow}{Feb 2023 - Feb 2025}{Fully-remote}

Mindflow is a startup providing a no-code SaaS automation platform for the cybersecurity industry.

\begin{itemize}
    \item Contributed to end-to-end development of platform features as a full-stack developer
    \begin{itemize}
        \item Collaborated closely with product teams and customers on feature design and improvements
        \item Developed front-end and back-end components, including automated unit/integration tests and manual QA.
        \item Managed cloud infrastructure, optimizing resources, handling incidents, and controlling costs.
    \end{itemize}
    \item Played a key role in onboarding and mentoring developers through pair programming, code reviews, and training sessions.
    \item Successfully led migration of the entire codebase to a monorepo architecture, significantly boosting team productivity and velocity.
    \item \textbf{Tech stack}: TypeScript, React, GraphQL, AWS, CDK.
\end{itemize}

\experience{Frontend developer}{Energisme}{Feb 2022 - Feb 2023}{Fully-remote}

Energisme manages a fleet of IoT devices dedicated to energy measurement, helping businesses and local governments reduce energy usage and carbon footprint.

\begin{itemize}
    \item Contributed to the development from scratch of an application ecosystem for collecting, visualizing, and leveraging energy measurement data.
    \item Tackled challenges related to code reuse and differentiated deployments across multiple clients and contexts.
    \item \textbf{Tech stack}: TypeScript, React, GraphQL, Azure, Java.
\end{itemize}

\experience{Frontend developer}{Bedrock Streaming}{Mar 2020 - Feb 2022}{Lyon, France}

Bedrock provides a white-label streaming platform for television channels and SVOD/AVOD services.

\begin{itemize}
    \item Developed applications for smart TVs (Samsung Tizen, LG webOS, etc.), addressing platform-specific performance constraints and proprietary components.
    \item Managed cloud infrastructure to support new requirements, resolve incidents, and optimize costs.
    \item Initiated an R\&D project to enable remote control of the TV fleet — originally designed to facilitate operations during the pandemic.
    \item \textbf{Tech stack}: JavaScript, React, Terraform, AWS.
\end{itemize}


\experience{Backend developer}{Michelin}{Jun 2019 - Feb 2020}{Lyon, France}

Michelin operates over a hundred commercial websites across multiple brands, languages, and customer segments (B2B and B2C).

\begin{itemize}
    \item Contributed to the operation of this large-scale website factory, focusing on back-end development and extending and maintaining the Apostrophe CMS.
    \item Worked within a multinational, multicultural team spread across three continents.
    \item \textbf{Tech stack}: Node.js, MongoDB, Apostrophe CMS.
\end{itemize}

\experience{DevOps Internship}{Zenika}{Sep 2018 - Feb 2019}{Lyon, France}
\vspace{-10pt}
\begin{itemize}
  \item Designed a reusable deployment stack, covering a full software development pipeline from Git repository to production environment.
  \item The goal was to deliver a plug-and-play DevOps solution enabling production deployment in under 5 minutes.
\end{itemize}

\experience{Webmaster, developer}{MesBilles.fr}{2016 - Current}{Fully-remote}
\vspace{-10pt}
\begin{itemize}
    \item Maintained and developed an e-commerce website initially built with PrestaShop.
    \item Created custom PHP modules and adapted existing ones to meet business needs.
    \item Improved SEO, accessibility, and site performance.
    \item Led a full migration to Shopify in 2022.
\end{itemize}

\cvsection{Education}

\experience{Peer-learning based coding program}{42 Paris}{2019}{}

\experience{Bachelor's degree in Mathematics and Computer Science (French \enquote{Licence} equivalent)}{Polytech Lyon}{2016}{}

\cvsection{Knowledge sharing}

\begin{itemize}
    \item \textbf{Training:} Alongside my client work, I have regularly delivered JavaScript training sessions — for both beginners and advanced developers — to diverse audiences ranging from younger students to corporate teams.
    \item \textbf{Presentations:} I've presented my work on numerous occasions, including internal conferences at Zenika and public meetups, such as those organized by the Cloud Native Computing Foundation (CNCF).
\end{itemize}



\cvsection{Skills and Interests}

\begin{itemize}
  \item \textbf{Languages:} French (native), English (bilingual)
  \item \textbf{Additional skills:} Strong IT culture and passion, self-directed learning, touch typing (120+ wpm), knowledge sharing and mentoring, agile methodologies
  \item \textbf{Interests:} Electronics, 3D printing, urban planning, rail and other mass-transit transport systems, cycling and hiking.
\end{itemize}

\end{document}
